Honey Bees - edgeR

### 2018-04-13 C_R/EdgeR/edgeR/makeDataMetrics.Rmd
Updated up and down regulated DEG counts

    df <- y[[1]][rownames(y[[1]]) %in% rownames(lrt5), c(which(sapply(colnames(y[[1]]), function(x) strsplit(x, "[.]")[[1]][1]) %in% (colnames(fit)[i])), which(sapply(colnames(y[[1]]), function(x) strsplit(x, "[.]")[[1]][1]) %in% (colnames(fit)[j])))]
    firstLarger <- length(which(apply(df, 1, function(x) mean(x[1:3]) > mean(x[4:6]))))
    secondLarger <- length(which(apply(df, 1, function(x) mean(x[1:3]) < mean(x[4:6]))))

>>>>

    df <- y[[1]][rownames(y[[1]]) %in% rownames(lrt5), c(which(sapply(colnames(y[[1]]), function(x) strsplit(x, "[.]")[[1]][1]) %in% (colnames(fit)[i])), which(sapply(colnames(y[[1]]), function(x) strsplit(x, "[.]")[[1]][1]) %in% (colnames(fit)[j])))]
    firstLarger <-  length(which(lrt5$logFC>0))
    secondLarger <-  length(which(lrt5$logFC<0))

### 2018-04-13 NC_NR_VC_VR/DESeq2/Method1/makeDataMetrics.Rmd
Updated up and down regulated DEG counts

    allPairs = rbind(allPairs, data.frame(Treatment1 = uTreat[i], Treatment2 = uTreat[j], NumberDEG = degLength, Treatment1Larger = t1Length, Treatment2Larger = t2Length))
  }
}
allPairs <- allPairs[order(allPairs$NumberDEG),]
allPairs
saveRDS(data, file="data.Rds")
saveRDS(dataMetrics, file="dataMetrics.Rds")
```

>>>>

    allPairs = rbind(allPairs, data.frame(Treatment1 = uTreat[i], Treatment2 = uTreat[j], NumberDEG = degLength, Treatment1Larger = t1Length, Treatment2Larger = t2Length))
  }
}
allPairs <- allPairs[order(allPairs$NumberDEG),]
allPairs
saveRDS(dataMetrics, file="dataMetrics.Rds")
```

### 2018-04-13 NC_NR_VC_VR/EdgeR/edgeR/makeDataMetrics.Rmd
Updated up and down regulated DEG counts

```{r}
minLib <- min(y$samples$lib.size)
nRep = length(lapply(colnames(beeCounts), function (x) unlist(strsplit(x, "[.]"))[1])) / length(unique(lapply(colnames(beeCounts), function (x) unlist(strsplit(x, "[.]"))[1])))
keep <- rowSums(cpm(y)>round(minLib/1000000)) >= nRep/2
# Number of genes 15,314--> 8,672
y <- y[keep, , keep.lib.sizes=FALSE]
```

@@

```{r}
allGroups <- c(rep("C",12), rep("R",12))
y$samples$group <- allGroups

@@

```{r}
Group = factor(c(rep("C",12), rep("R",12)))
design <- model.matrix(~0+Group, data=y$samples)
colnames(design) <- levels(Group)
y <- estimateDisp(y, design)
plotBCV(y)
```

>>>>

```{r}
minLib <- min(y$samples$lib.size)
keep <- rowSums(cpm(y)>4) >= 6
# Number of genes 15,314--> 8,672
y <- y[keep, , keep.lib.sizes=FALSE]
```

@@

```{r}
allGroups <- c(rep("NC",6), rep("NR",6), rep("VC",6), rep("VR",6))
y$samples$group <- allGroups

@@

```{r}
Group = factor(c(rep("NC",6), rep("NR",6), rep("VC",6), rep("VR",6)))
targets <- data.frame(rownames=paste0("Sample",1:24), Virus = c(rep("N",12), rep("V",12)), Diet = c(rep("C",6), rep("R",6), rep("C",6), rep("R",6)), Group = Group)
design <- model.matrix(~0+Group, data=y$samples)
colnames(design) <- levels(Group)
y <- estimateDisp(y, design)
plotBCV(y)
```
